HealpixNet: Efficient spherical Convolutional Neural Network with Healpix sampling for cosmological applications

### 2018-08-08 scnn.tex
finish pass on Appendix

    \item (MD+NP) talk about the loss in 3.8 (old 4.8)
    \item (done!) (NP) make figure A.13 remove white space
    \item (firsr version done!)(NP+MD)  paragraph on our chosen architecture in the Experiments sections
    \item (Done) (NP) vertex interpretation 
    \item (MD) Are you happy with the vertex interpretation in section 3.5 Efficient convolutions? Also do you like the end of 3.4?
    \item (NP) Finalise readme on Github code
    \item branch with notebooks with plots (results) NP
    \item NP move the repo to HealpixNet
    \item check if papers which appear as arxiv were not published in a conference or journal
    \item MD add irregular (random) sampling to comparison with spherical harmonics? Could motivate people to think about different samplings. \nati{I think this is too much for this paper.}
    \item TK check part sphere notebook and whole sphere
    \item (done!) (TK) update the README for data zip - file from NP
    \item (almost done) TK read everything
    \item (done!) (TK) uniformize text size in figures
    \item (done!) (TK) add small description of maps\_downsampled\_64.npz in the whole\_sphere notebook. \nati{We need to talk about that.}
    \item (done!) (TK) re-make figures to make the labels/legend/titles the same font size as the main text
    \item (done!) TK check the appendix
    \item (done!) TK optional - example of data (CMB (mask) + mass map + radio intensity)
    \item (done!) (TK) add info on comparison with histograms, so that it's just a demonstration
    \item (done!) TK read the result section
    \item (done!) (TK) add reference to figure (pooling) to the area of orders
    \item (done!) (TK) add section in conclusions/ paragraph on possible extensions to the code: dense output, regression, GANs, segmentation
    % \item (TK took exec decision and moved it :D) Should the heat example go to appendix?
    % \item (done! first version done) conclusions
    % \item (done!) Michael section 4.5 (efficient convolutions) and 3.2 (conv on graphs)
    % \item (done!) (TK NP) if we have time make a new candidate for network plot (optional)
    % \item (done!) TK read the heat section again
    % \item (done!) (TK) make a new proposition for a plot Figure 6: Two levels of coarsening and pooling
    % \item \todo{Notation GC32 - P256 - FC10 to describe an architecture? Maybe more useful in Experiments where we describe the architecture used for each experiment.}
    % Nati: I did it without this notation. Since we have two architectures, I think it is OK.
\end{itemize}

@@

We show that the modelling the discretised sphere by a graph enables an efficient convolution operation on HEALPix sampling.
% Hence, it relaxes the iso-latitude constraint on sampling schemes who aim to enable fast convolutions.
% \TK{I would move the info about possible relaxation of the iso-latitude thing to a separate paragraph at the end on conclusions - future prospects?}
Graph-based representation of the sphere can display small imprecisions in rotation invariance, the result of which is that an action of a graph filter slightly depends on the location.
For applications that can tolerate this property, a graph-based representation may be a worthwhile alternative.
% this relaxation might enable researchers to consider sampling sets with different properties.
% \TK{this I don't understand}
For example, a machine learning based cosmological inference algorithm can in principle tolerate this property, as it requires the simulations to be represented the same way as observations anyway.
This way, imperfections in representation will affect the simulations and real data in the same way, and will not cause biases in the analysis result.

@@

\section*{Acknowledgements}
This work was supported by a grant from the Swiss Data Science Centre (SDCS) under project ID \textit{sd01 - DLOC:  Deep Learning for Observational Cosmology} and grant number 200021\_169130 from the Swiss National Science Foundation.

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
\appendix

@@

When comparing the network to the baselines, we want to ensure that the SVM classifier has
access to the same amount of data that the network, i.e, potentially an
infinite number of samples. Hence, we fit different linear SVM classifiers using
various training set size until we observe experimentally that
increasing the amount of data does not improve the accuracy. The validation
set remain the same and is used for cross-validation to tune the L2
penalization parameter of SVM. Eventually, we evaluate the final classifier on
the testing set. An example of the evolution of the training and valdication
error is shown in \figref{hist_error_evolution}.

>>>>

    \item (MD+NP) talk about the loss in 3.8 (old 4.8)
    \item (done!) (NP) make figure A.13 remove white space
    \item (first version done!)(NP+MD) paragraph on our chosen architecture in the Experiments sections
    \item (Done) (NP) vertex interpretation 
    \item (MD) Are you happy with the vertex interpretation in section 3.5 Efficient convolutions? Also do you like the end of 3.4?
    \item (NP) Finalise readme on Github code
    \item branch with notebooks with plots (results) NP
    \item NP move the repo to HealpixNet
    \item check if papers which appear as arxiv were not published in a conference or journal
    \item MD add irregular (random) sampling to comparison with spherical harmonics? Could motivate people to think about different samplings. \nati{I think this is too much for this paper.}
    \item TK check part sphere notebook and whole sphere
    \item (done!) (TK) update the README for data zip - file from NP
    \item (almost done) TK read everything
    \item (done!) (TK) uniformize text size in figures
    \item (done!) (TK) add small description of maps\_downsampled\_64.npz in the whole\_sphere notebook. \nati{We need to talk about that.}
    \item (done!) (TK) re-make figures to make the labels/legend/titles the same font size as the main text
    \item (done!) TK check the appendix
    \item (done!) TK optional - example of data (CMB (mask) + mass map + radio intensity)
    \item (done!) (TK) add info on comparison with histograms, so that it's just a demonstration
    \item (done!) TK read the result section
    \item (done!) (TK) add reference to figure (pooling) to the area of orders
    \item (done!) (TK) add section in conclusions/ paragraph on possible extensions to the code: dense output, regression, GANs, segmentation
    % \item (TK took exec decision and moved it :D) Should the heat example go to appendix?
    % \item (done! first version done) conclusions
    % \item (done!) Michael section 4.5 (efficient convolutions) and 3.2 (conv on graphs)
    % \item (done!) (TK NP) if we have time make a new candidate for network plot (optional)
    % \item (done!) TK read the heat section again
    % \item (done!) (TK) make a new proposition for a plot Figure 6: Two levels of coarsening and pooling
    % \item \todo{Notation GC32 - P256 - FC10 to describe an architecture? Maybe more useful in Experiments where we describe the architecture used for each experiment.}
    % Nati: I did it without this notation. Since we have two architectures, I think it is OK.
\end{itemize}

@@

We show that the modeling the discretised sphere by a graph enables an efficient convolution operation on HEALPix sampling.
% Hence, it relaxes the iso-latitude constraint on sampling schemes who aim to enable fast convolutions.
% \TK{I would move the info about possible relaxation of the iso-latitude thing to a separate paragraph at the end on conclusions - future prospects?}
Graph-based representation of the sphere can display small imprecisions in rotation invariance, the result of which is that an action of a graph filter slightly depends on the location.
For applications that can tolerate this property, a graph-based representation may be a worthwhile alternative.
% this relaxation might enable researchers to consider sampling sets with different properties.
% \TK{this I don't understand}
For example, a machine learning based cosmological inference algorithm can in principle tolerate this property, as it requires the simulations to be represented the same way as observations anyway.
This way, imperfections in representation will affect the simulations and real data in the same way, and will not cause biases in the analysis result.

@@

\section*{Acknowledgements}
This work was supported by a grant from the Swiss Data Science Centre (SDCS) under project ID \textit{sd01 - DLOC:  Deep Learning for Observational Cosmology} and grant number 200021\_169130 from the Swiss National Science Foundation.
\nati{@Tomek: do we need to thank Janis?}
%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
\appendix

@@

When comparing the network to the baselines, we want to ensure that the SVM classifier has
access to the same amount of data than the network, i.e, potentially an
infinite number of samples. Hence, we fit different linear SVM classifiers using
various training set size until we experimentally observe that
increasing the amount of data does not improve the accuracy. The validation
set remain the same and is used for cross-validation to tune the L2
penalization parameter of SVM. Eventually, we evaluate the final classifier on
the testing set. An example of the evolution of the training and valdication
error is shown in \figref{hist_error_evolution}.
